Технология использования открытых данных Федеральной налоговой службы России для экономико-географического анализа

### 2024-05-20 legal-services-provision/journal-article/Article.Rmd
Rename folder, #2

Figure 4 presents a map of cities with relatively high (more than 5 lawyers per 10,000 people) provision of legal services. The most prominent cluster is formed by Moscow and its satellite cities. Other notable cities with high provision include Krasnodar and Stavropol in the south of Russia, Yekaterinburg and Chelyabinsk in the Urals, and Tyumen and Novosibirsk in Western Siberia, as well as Irkutsk in Eastern Siberia. There are several regions with no cities that provide a high level of legal services provision (in particular, the Far East, North, and Caucasus). Conversely, the majority of cities with a relatively high level of legal services provision are located in five economic regions of the country (as categorized by @Leyzerovich2010): Central, Central-Chernozem, Volga-Vyatka, Volga, Ural.

@@

The provision of legal services in cities has a positive relationship with the number of lawyers. The overall trend can be approximated by a square root curve, while the relationship in distinct population size groups is close to linear with varying slope of the regression line. In small cities the increase in the number of lawyers has a minimal impact on the level of legal services provision, given the considerable variation of the dependent variable. In larger cities, the relationship is linear and positive. In the cities with a population above one million, the impact of the growth of the number of lawyers on the provision of legal services is less pronounced, as the latter is already high and uniform in these cities. Regional centers typically have a relatively high availability of legal services. Moscow and Saint Petersburg are distinguished by the highest number of lawyers and the high provision of legal services. Empirical data indicates that there may be a saturation limit beyond which the increase in the number of employees at law firms does not have a substantial impact on the provision of legal services

The majority of cities (approximately 85%) are characterized by a paucity of lawyers and a correspondingly limited level of legal services provision. Two distinct groups of cities can be identified based on their approach to achieving high level of legal services provision. The first group is comprised of cities with large number of lawyers. The second group, in contrast, has small number of lawyers that nevertheless meet the needs of local communities. Moscow and its surrounding region exhibit a relatively high level of legal services provision, as do the Central and Volga economic regions of Russia. Similarly, Saint Petersburg, Krasnodar, Stavropol, Yekaterinburg, Chelyabinsk, Tyumen, and Novosibirsk also have a satisfactory provision of legal services. Conversely, in numerous regions of the Far East, North and Caucasus the provision of legal services is notably limited.

>>>>

Figure 4 presents a map of cities with relatively high (more than 5 lawyers per 10,000 people) provision of legal services. The most prominent cluster is formed by Moscow and its satellite cities. Other notable cities with high provision include Krasnodar and Stavropol in the south of Russia, Yekaterinburg and Chelyabinsk in the Urals, and Tyumen and Novosibirsk in Western Siberia, as well as Irkutsk in Eastern Siberia. There are several regions with no cities that provide a high level of legal services provision (in particular, the Far East, North, and Caucasus). Conversely, the majority of cities with a relatively high level of legal services provision are located in five economic regions of the country, as categorized by @Leyzerovich2010: Central, Central-Chernozem, Volga-Vyatka, Volga, Ural.

@@

The provision of legal services in cities has a positive relationship with the number of lawyers. The overall trend can be approximated by a square root curve, while the relationship in distinct population size groups is close to linear with varying slope of the regression line. In small cities the increase in the number of lawyers has a minimal impact on the level of legal services provision. In larger cities, the relationship is linear and positive. In the cities with a population above one million, the impact of the growth of the number of lawyers on the provision of legal services is less pronounced, as the latter is already high and uniform in these cities. Regional centers typically have a relatively high availability of legal services. Moscow and Saint Petersburg are distinguished by the highest number of lawyers and the high provision of legal services. Empirical data indicates that there may be a saturation limit beyond which the increase in the number of employees at law firms does not have a substantial impact on the provision of legal services

The majority of cities (approximately 85%) are characterized by a paucity of lawyers and a correspondingly limited level of legal services provision. Two distinct groups of cities can be identified based on their approach to achieving high level of legal services provision. The first group is comprised of cities with large number of lawyers. The second group, in contrast, has small number of lawyers that nevertheless meet the needs of local communities. Moscow and its surrounding region exhibit a relatively high level of legal services provision. Similarly, Saint Petersburg, Krasnodar, Stavropol, Yekaterinburg, Chelyabinsk, Tyumen, Novosibirsk, and Irkutsk also have a satisfactory provision of legal services. Most of the cities with high level of legal services provision are situated within five economic regions of the country: Central, Central-Chernozem, Volga-Vyatka, Volga, and Ural. Conversely, in numerous regions of the Far East, North and Caucasus the provision of legal services is notably limited.
